Mixed effect tweedie model in TMB

### 2019-04-12 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
update calls to cross validation code

>>>>

10-fold cross-validation of candidate models
```{r}
temp1 <- loglik_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year) + depth_scaled,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp1$sum_loglik)

temp2 <- loglik_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp2$sum_loglik)

temp3 <- loglik_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2 + depth_scaled3,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp3$sum_loglik)

# allow slope with depth to vary through between years with a random walk
temp1_rw <- loglik_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp1_rw$sum_loglik)

temp2_rw <- loglik_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled + depth_scaled2,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp2_rw$sum_loglik)

temp3_rw <- loglik_cv(data = d_trawl, n_knots = 30, x = "X", y ="Y", k_folds = 5, plot_spde = TRUE,
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp3_rw$sum_loglik)
```
